---
title: "Business Intelligence Project"
author: "Lakers"
date: "6th November 2023"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---
# Student Details

+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Student ID Numbers and Names of Group Members** 
|                                                   |                                                                                                                                                                          |
|                                                   | 1.  134780 - C - Trevor Okinda                                                                                                                                              |
|                                                   |                                                                                                                                                                          |
|                                                   | 2.  132840 - C - Sheila Wangui                                                                                                                                              |
|                                                   |                                                                                                                                                                          |
|                                                   | 3.  131749 - C - Teresia Nungari                                                                                                                                              |
|                                                   |                                                                                                                                                                          |
|                                                   | 4.  135203 - C - Tom Arnold                                                                                                                                              |
|                                                   |                                                                                                                                                                          |
|                                                   |                                                                                                                                              |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **GitHub Classroom Group Name**                   | Lakers                                                                                                       
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Course Code**                                   | BBT4206                                                                                                                                                                  |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Course Name**                                   | Business Intelligence II                                                                                                                                                 |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Program**                                       | Bachelor of Business Information Technology                                                                                                                              |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Semester Duration**                             | 21^st^ August 2023 to 28^th^ November 2023                                                                                                                               |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+



# Setup Chunk


**Note:** the following KnitR options have been set as the global defaults: <BR> `knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(
  warning = FALSE,
  collapse = FALSE
)
```
# STEP 1. Install and Load the Required Packages ----
#Load the language server first
```{r}

if (require("languageserver")) {
  require("languageserver")
} else {
  install.packages("languageserver", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}
## mlbench ----
if (require("mlbench")) {
  require("mlbench")
} else {
  install.packages("mlbench", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}
## caret ----
if (require("caret")) {
  require("caret")
} else {
  install.packages("caret", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## kernlab ----
if (require("kernlab")) {
  require("kernlab")
} else {
  install.packages("kernlab", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## randomForest ----
if (require("randomForest")) {
  require("randomForest")
} else {
  install.packages("randomForest", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}
```
# Load necessary libraries
library(caret)
library(e1071)
library(randomForest)
library(kernlab)
library(rpart)

# Load the Iris dataset (this dataset is included in R)
data(iris)

#Train the models
# Define train control
train_control <- trainControl(method = "repeatedcv", number = 10, repeats = 3)

### LDA ----
set.seed(7)
iris_model_lda <- train(Species ~ ., data = iris,
                        method = "lda", trControl = train_control)
### CART ----
set.seed(7)
iris_model_cart <- train(Species ~ ., data = iris,
                         method = "rpart", trControl = train_control)
### KNN ----
set.seed(7)
iris_model_knn <- train(Species ~ ., data = iris,
                        method = "knn", trControl = train_control)
### SVM ----
set.seed(7)
iris_model_svm <- train(Species ~ ., data = iris,
                        method = "svmRadial", trControl = train_control)
### Random Forest ----
set.seed(7)
iris_model_rf <- train(Species ~ ., data = iris,
                       method = "rf", trControl = train_control)
## Call the `resamples` Function ----
results <- resamples(list(LDA = iris_model_lda, CART = iris_model_cart,
                          KNN = iris_model_knn, SVM = iris_model_svm,
                          RF = iris_model_rf))

## 1. Table Summary ----
summary(results)

## 2. Box and Whisker Plot ----
scales <- list(x = list(relation = "free"), y = list(relation = "free"))
bwplot(results, scales = scales)

## 3. Dot Plots ----
dotplot(results, scales = scales)

## 4. Scatter Plot Matrix ----
splom(results)

## 5. Pairwise xyPlots ----
xyplot(results, models = c("LDA", "SVM"))
xyplot(results, models = c("SVM", "CART"))

## 6. Statistical Significance Tests ----
diffs <- diff(results)

summary(diffs)
